---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(canrecall)
```

# canrecall is an API wrapper for the Canadian Recalls and Safety Alerts API.

There are three main functions present in canrecall.

### recall_api : used to parse recall data. The result is a dataframe

There are 4 filters:

  category: an integer variable where 1 = FOOD, 2 = VEHICLES, 3 = HEALTH PRODUCTS, 4 = CONSUMER PRODUCTS
  lang: a string variable as 'en' = English, 'fr' = French for response language
  lim: an integer variable to limit results to n
  search: a string variable to search the database for
  
So, for the most recent 10 results for peanuts, in english, the function would look like:

recall_api('peanuts', 'en', 1, 10)

### recall_api_date : similar to recall_api, but meant to parse recall searches by date. The result is a dataframe

Here, there are 5 filters:

  category: an integer variable where 1 = FOOD, 2 = VEHICLES, 3 = HEALTH PRODUCTS, 4 = CONSUMER PRODUCTS
  lang: a string variable as 'en' = English, 'fr' = French for response language
  datestart: a string variable for the lower date bound of the search
  dateend: a string variable for the upper date bound of the search
  search: a string variable to search the database for

So, to find recall data for peanuts, in english, in 2018, the function would look like:

recall_api('peanuts', 'en, 1, '1/1/2018','12/31/2018')

### recall_api_recent : regardless of fitler, retrieves the 15 most recent recalls.


Documentation for the API can be found at https://healthycanadians.gc.ca/connect-connectez/data-donnees/recall-alert-rappel-avis-eng.php



